Empowering Multi-Span Question Answering with Expansive Information Injection using Large Language Models

### 2024-03-31 method.tex
update method

\subsubsection{Model Ensemble}
\label{sec:model_ensemble}

>>>>

\subsubsection{Model Ensemble}
\label{sec:model_ensemble}
 From the model ensemble perspective, we first fine-tune multiple single-knowledge-enhanced question-answering models. During the prediction phase, each model performs token-based B/I/O classification on the context. Subsequently, for each token, we conduct a voting process on the prediction results from each model, selecting the category with the highest number of votes as the final classification result. In case of a tie, we compare the average probabilities of all categories provided by the models, and select the category with the higher average probability as the classification for the given token.

 Overall, we applied the aforementioned integration methods to two combinations for research purposes:$(a)$ combining factual knowledge (entity interpretation, entity relationships) with content continuation to compare the effectiveness of model ensemble methods versus data ensembles methods in knowledge fusion; and $(b)$ combining factual knowledge, content continuation, and other data augmentation methods (such as LIQUID) to investigate the compatibility between the model and other data augmentation methods.
